Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-15 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
更新图表

\begin{figure}
\centering
\subfigure{\includegraphics[width=0.2\textwidth]{images/x.jpg}} \qquad
\subfigure{\includegraphics[width=0.2\textwidth]{images/z.jpg}}
\caption{Left: search patch. Right: template disturb.}
\end{figure}

@@

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\textwidth]{images/network.pdf}
\caption{network structure}
\end{figure*}

@@

\begin{algorithm}[tb]
\caption{Example algorithm}
\label{alg:algorithm}
\textbf{Input}: Videos $V$, Siamese tracker $T$, max iteration $N$\\
\textbf{Parameter}: Universal perturbation $\delta$ and universal patch $\sigma$.\\
\textbf{Output}: Universal perturbation $\delta$ and universal patch $\sigma$.
\begin{algorithmic}[1] %[1] enables line numbers
\STATE Let $\delta=0, \sigma=0, i = 0$.
\WHILE{$i < N$}
\STATE random pick a video $v\in V$.
\STATE random pick two frames $I_i, I_j$ from $v$.
\STATE generate template image $z = f(I_i)$.
\STATE generate search image $x = f(I_j)$.
\STATE generate perturbed template image $\tilde z = z + \delta$
\STATE generate perturbed search image $\tilde x = A(x, \sigma)$
\STATE generate prediction $y = F(\tilde x, \tilde z)$
\STATE generate fake ground truth $\hat y = B(A)$
\STATE $\delta = \delta - \epsilon_1\cdot\text{sign}(\nabla_{\delta}L(y, \hat y))$
\STATE $\sigma = \sigma - \epsilon_2 \cdot \text{sign}(\nabla_{\sigma}L(y, \hat y))$
\STATE $i = i + 1$
\IF {conditional}
\STATE Perform task A.
\ELSE
\STATE Perform task B.
\ENDIF
\ENDWHILE
\STATE \textbf{return} solution
\end{algorithmic}
\end{algorithm}

@@

\begin{table}[h]
\centering
\resizebox{0.4\textwidth}{!}{%
\begin{tabular}{ccc|cccc}
\toprule
$L_{cls}$ & $L_{quality}$ & $L_{reg}$ & FGT AO & FGT SR50 & GT AO & GT SR50 \\ \midrule
\checkmark   &    &    & 0.718  & 0.824    & 0.086 & 0.083   \\
   & \checkmark   &    & 0.044  & 0.044    & 0.703 & 0.842   \\
   &    & \checkmark   & 0.664  & 0.726    & 0.165 & 0.184   \\
\checkmark   & \checkmark   & \checkmark   & 0.781  & 0.855    & 0.071 & 0.066   \\ \bottomrule
\end{tabular}}
\caption{Different loss weight.}
\end{table}

@@

\begin{table}[h]
\centering
\resizebox{0.45\textwidth}{!}{%
\begin{tabular}{c|cc|cc}
\toprule
Trackers     & Succ-ORI & Prec-ORI & Succ-ATTACK & Precision-ATTACK \\ \midrule
siamRPN++    & 0.676   & 0.879     & 0.518       & 0.691 \\
SiamRPN      & 0.666   & 0.876     & 0.379       & 0.506 \\ \bottomrule
\end{tabular}%
}
\caption{Transferability of different architecture on OTB2015}
\end{table}

>>>>

@@

\begin{figure}[htbp]
\centering
%\subfigure{\includegraphics[width=0.2\textwidth]{images/x.jpg}} \qquad
%\subfigure{\includegraphics[width=0.2\textwidth]{images/z.jpg}}
\includegraphics[width=0.4\textwidth]{images/1_v3.pdf}
\caption{Our approach generates the universal perturbations which can be used to attack the Siamese tracker on any video in a targeted manner. Our approach allows perturbing a new video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimisation or network inference.}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=1.0\textwidth]{images/network_v2.pdf}
\caption{The pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target.}
\end{figure*}

@@

\begin{algorithm}[tb]
\caption{Example algorithm}
\label{alg:algorithm}
\textbf{Input}: Videos $V$, Siamese tracker $T$, max iteration $N$\\
\textbf{Parameter}: Universal perturbation $\delta$ and universal patch $\sigma$.\\
\textbf{Output}: Universal perturbation $\delta$ and universal patch $\sigma$.
\begin{algorithmic}[1] %[1] enables line numbers
\STATE Let $\delta=0, \sigma=0, i = 0$.
\WHILE{$i < N$}
\STATE random pick a video $v\in V$.
\STATE random pick two frames $I_i, I_j$ from $v$.
\STATE generate template image $z = f(I_i)$.
\STATE generate search image $x = f(I_j)$.
\STATE generate perturbed template image $\tilde z = z + \delta$
\STATE generate perturbed search image $\tilde x = A(x, \sigma)$
\STATE generate prediction $y = F(\tilde x, \tilde z)$
\STATE generate fake ground truth $\hat y = B(A)$
\STATE $\delta = \delta - \epsilon_1\cdot\text{sign}(\nabla_{\delta}L(y, \hat y))$
\STATE $\sigma = \sigma - \epsilon_2 \cdot \text{sign}(\nabla_{\sigma}L(y, \hat y))$
\STATE $i = i + 1$
\ENDWHILE
\STATE \textbf{return} solution
\end{algorithmic}
\end{algorithm}

@@

\begin{table}[h]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{ccc|cc|cc} 
\toprule
\multirow{2}{*}{$L_{cls}$}     & \multirow{2}{*}{$L_{quality}$} & \multirow{2}{*}{$L_{reg}$} & \multicolumn{2}{c|}{Fake Trajectory}          & \multicolumn{2}{c}{Real Trajectory}           \\ 
\cmidrule{4-7}
                       &                    &                    & AO                    & SR                    & AO                    & SR                     \\ 
\midrule
\checkmark   &    &    & 0.718  & 0.824    & 0.086 & 0.083   \\
   & \checkmark   &    & 0.044  & 0.044    & 0.703 & 0.842   \\
   &    & \checkmark   & 0.664  & 0.726    & 0.165 & 0.184   \\
\checkmark   & \checkmark   & \checkmark   & 0.781  & 0.855    & 0.071 & 0.066   \\ \bottomrule
\end{tabular}
}
\caption{Different loss weight.}
\end{table}

@@

\begin{table}[ht]
\centering
\resizebox{0.48\textwidth}{!}{%
\begin{tabular}{c|cc|cc} 
\toprule
\multirow{2}{*}{Trackers} & \multicolumn{2}{c|}{Clean Videos} & \multicolumn{2}{c}{Perturbed Videos}  \\
\cmidrule{2-5}
                          & Success & Precision              & Success & Precision                   \\
\midrule
SiamRPN++                 & 0.676   & 0.879                  & 0.518   & 0.691                       \\
SiamRPN                   & 0.666   & 0.876                  & 0.379   & 0.506                       \\
\bottomrule
\end{tabular}
}
\caption{Transferability of different architecture on OTB2015}
\end{table}
